Domain-Driven, Generative Data Model for BigPetStore

### 2014-07-21 bdcloud_paper/latex/paper.tex
Added intro paragraph to model

\section{Overview of Model \& Simulation Procedures}

\textcolor{red}{need an intro paragrpah}

>>>>

\section{Overview of Model \& Simulation Procedures}
Our generatorive model combines various well-known mathematical modeling techniques to simulate the factors affecting customers' purchasing habits.  Each part of the model is derived from \emph{ab initio} assumptions.  In several cases, real data is used to parameterize parts of the model.

\textcolor{red}{relational data model diagram?}
